---
output: reprex::reprex_document
knit: reprex::reprex_render
---

Notebook to run STURM Ouput.

```{r}
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)

print(paste("Working directory is:", getwd()))

# Loding figures setttings and functions
source("STURM_output/C00_plots.R")


run_test <- FALSE
if (run_test) {
      run <- "scenarios_test"
      scenarios <- c(
        "EU_exogenous" = "Baseline",
        "EU_constant_exogenous" = "Price constant",
        "EU_price_2020_600_exogenous" = "Carbon tax",
        "EU_no_exogenous" = "No renovation",
        "EU_no_constant_exogenous" = "No renovation, Price constant",
        "EU_double_exogenous" = "Doubling renovation",
        "EU_double_constant_exogenous" =
          "Doubling renovation, Price constant",
        "EU_triple_exogenous" = "Tripling renovation",
        "EU_triple_constant_exogenous" =
          "Tripling renovation, Price constant",
        "EU_emission_1p5c_exogenous" = "Low emission factor",
        "EU_double_emission_1p5c_exogenous" =
          "Doubling renovation, Low emission factor",
        "EU_1p5c_exogenous" = "1p5C"
    )
      scenarios <- c(
        "EU_no_exogenous" = "No renovation",
        "EU_exogenous" = "Baseline",
        "EU_double_exogenous" = "Doubling renovation",
        "EU_double_emission_1p5c_exogenous" = "Doubling renovation, 1p5c")

      colors_scenarios <- c(
        "Price constant" = "#247f6e",
        "Doubling renovation" = "#ee6a6b",
        "Doubling renovation, Price constant" = "#531717",
        "Doubling renovation, 1p5c" = "#1f540b",
        "Tripling renovation" = "#380707",
        "Tripling renovation, Price constant" = "#531717",
        "No renovation" = "#6a4c93",
        "No renovation, Price constant" = "#531717"
      )
    } else {
    run <- "scenarios_detail"

    scenarios <- c(
        "EU" = "Current policies",
        "EU_reno_wave" = "Renovation wave",
        "EU_deep_reno_wave" = "Deep Renovation wave",
        "EU_carbon_tax" = "Carbon tax",
        "EU_carbon_tax_ambitious" = "Carbon tax ambitious",
        "EU_heat_pump" = "Climate Fund",
        "EU_heat_pump_ambitious" = "Climate Fund ambitious"
    )

    run <- "scenarios_report"

    scenarios <- c(
        "EU" = "Current policies",
        "EU_mix" = "Base Mix",
        "EU_mix_ambitious" = "Enhanced Mix",
        "EU_mix_ban" = "Fossil-Ban Mix"
    )
  }

colors_scenarios <- c(
  "Current policies" = "#00111c",
  "Base Mix" = "#014f86",
  "Enhanced Mix" = "#057a55",
  "Fossil-Ban Mix" = "#d45113"
  )

line_styles_scenarios <- c(
  "Current policies" = "solid",
  "Proposed Mix" = "solid",
  "Enhanced Mix" = "dotted",
  "Fossil-Ban Mix" = "dotdash"
)
```

## Read data
```{r}
save_dir <- paste("STURM_output", "figures", run, sep = "/")
if (!dir.exists(save_dir)) {
  dir.create(save_dir)
}

data <- data.frame(NULL)

for (scenario in names(scenarios)) {
  print(paste("Scenario:", scenario))
  file <- paste0("report_agg_STURM_", scenario, "_resid_region_bld_energy.csv")
  file <- paste("STURM_output/results", file, sep = "/")

  if (!file.exists(file)) {
    print("Check file name or directory!")
  }

  # Read output files
  temp <- read.csv(file) %>%
    mutate(scenario = scenario)
  
  data <- bind_rows(data, temp)
}
# Reconstuction flows
flows <- c("n_renovation", "cost_renovation_EUR", "sub_renovation_EUR",
  "n_replacement", "cost_heater_EUR", "sub_heater_EUR",
  "to_pay_renovation", "to_pay_heater")

data <- data %>%
  mutate(scenario = scenarios[.data[["scenario"]]])

stp <- 5

data <- data %>%
 mutate(year = ifelse(variable %in% flows, year - stp, year),
        value = ifelse(variable %in% flows, value / stp, value))
data <- distinct(data)
```

## Processing output
### Table summary
```{r}
source("STURM_output/C00_plots.R")

ref <- "Current policies"
base_year <- 2015

temp <- output_table(data, save_dir = save_dir, end_year = 2050, base_year = 2015)
format_temp <- temp$format_temp
output_table(data, save_dir = save_dir, end_year = 2030, base_year = 2015)

format_temp_eu <- format_temp %>%
  filter(Scenario != "Initial") %>%
  filter(`Member states` == "EU") %>%
  mutate(`Energy poverty (Percent)` = `Energy poverty (Percent)` * 100) %>%
  mutate(`Cost total (Billion EUR)` =
    `Cost renovation (Billion EUR)` + `Cost heater (Billion EUR)`) %>%
  mutate(`Cost total (Billion EUR per year)` =
    `Cost total (Billion EUR)` / 35) %>%
  mutate(Scenario = factor(Scenario), levels = unname(Scenario))

````
```{r}
source("STURM_output/C00_plots.R")

legend <- TRUE
presentation <- FALSE
scatter_plots(format_temp_eu,
              "Emission (MtCO2)",
              "Energy poverty (Percent)",
              color_column = "Scenario",
              colors_scenarios = colors_scenarios,
              size_column = "Cost total (Billion EUR per year)",
              legend_suffix = "B€/year",
              save_path = paste(save_dir,
                paste0(run, "_tCO2_poverty_eu.png"), sep = "/"),
              y_label_suffix = "%",
              x_label_suffix = "MtCO2",
              legend = legend,
              presentation = presentation,
              y_label = "Share of population in energy poverty",
              x_label = "Space heating emission (scope 2)"
              )
```

## Figure
## Figures comparison scenario
### Dwelling units by fuel type
```{r}
source("STURM_output/C00_plots.R")

var <- "stock_building"
years <- c(2015, 2030, 2050)
sub_scenarios <- c(
  "Current policies" = "Current policies",
  "Base Mix" = "Base",
  "Enhanced Mix" = "Enhanced",
  "Fossil-Ban Mix" = "Fossil-Ban")

df <- data %>%
  filter(scenario %in% names(sub_scenarios)) %>%
  mutate(scenario = sub_scenarios[.data[["scenario"]]]) %>%
  filter(resolution %in% names(rename_fuels)) %>%
  filter(variable == var) %>%
  filter(region_bld == "EU") %>%
  filter(year %in% years) %>%
  mutate(value = value / 1e6)

plot_clustered_barplot(df,
  "scenario",
  "resolution",
  y_label = "Dwelling units in the EU by fuel type",
  y_label_suffix = "Million",
  display_total = FALSE,
  x_order = sub_scenarios,
  angle_x_label = 90,
  save_path = paste(save_dir, paste0(run, "_dwelling_fuel_year_scenario_stack.png"), sep = "/"))

```

### Dwelling units by energy efficiency
```{r}
source("STURM_output/C00_plots.R")

var <- "stock_building"
years <- c(2015, 2030, 2050)

df <- data %>%
  filter(scenario %in% names(sub_scenarios)) %>%
  mutate(scenario = sub_scenarios[.data[["scenario"]]]) %>%
  filter(resolution %in% names(rename_eneff)) %>%
  filter(variable == var) %>%
  filter(region_bld == "EU") %>%
  filter(year %in% years) %>%
  mutate(value = value / 1e6)

plot_clustered_barplot(df,
  "scenario",
  "resolution",
  y_label = "Dwelling units in the EU by fuel type",
  y_label_suffix = "Million",
  display_total = FALSE,
  x_order = sub_scenarios,
  angle_x_label = 90,
  save_path = paste(save_dir, paste0(run, "_dwelling_eff_year_scenario_stack.png"), sep = "/"))

```

### Dwelling units by insulation_level
```{r}
source("STURM_output/C00_plots.R")

var <- "stock_building"
years <- c(2015, 2030, 2050)

df <- data %>%
  filter(scenario %in% names(sub_scenarios)) %>%
  mutate(scenario = sub_scenarios[.data[["scenario"]]]) %>%
  filter(resolution %in% names(rename_insulation)) %>%
  filter(variable == var) %>%
  filter(region_bld == "EU") %>%
  filter(year %in% years) %>%
  mutate(value = value / 1e6)

plot_clustered_barplot(df,
  "scenario",
  "resolution",
  y_label = "Dwelling units in the EU by fuel type",
  y_label_suffix = "Million",
  display_total = FALSE,
  x_order = sub_scenarios,
  angle_x_label = 90,
  save_path = paste(save_dir, paste0(run, "_dwelling_eff_year_scenario_stack.png"), sep = "/"))

```
### Space heating consumption by fuel type and scenario
```{r}
source("STURM_output/C00_plots.R")

var <- "heat_kWh"
years <- c(2015, 2030, 2050)

df <- data %>%
  filter(scenario %in% names(sub_scenarios)) %>%
  mutate(scenario = sub_scenarios[.data[["scenario"]]]) %>%
  filter(resolution %in% names(rename_fuels)) %>%
  filter(variable == var) %>%
  filter(region_bld == "EU") %>%
  filter(year %in% years) %>%
  mutate(value = value / 1e9)

plot_clustered_barplot(df,
  "scenario",
  "resolution",
  y_label = "Space heating consumption in the EU by fuel type",
  y_label_suffix = "TWh",
  display_total = TRUE,
  x_order = sub_scenarios,
  angle_x_label = 90,
  save_path = paste(save_dir, paste0(run, "_kWh_year_scenario_stack.png"), sep = "/"))

```
### Space heating emission by fuel type and scenario
```{r}
source("STURM_output/C00_plots.R")

var <- "heat_tCO2"
df <- data %>%
  filter(scenario %in% names(sub_scenarios)) %>%
  mutate(scenario = sub_scenarios[.data[["scenario"]]]) %>%
  filter(resolution %in% names(rename_fuels)) %>%
  filter(variable == var) %>%
  filter(region_bld == "EU") %>%
  filter(year %in% years) %>%
  mutate(value = value / 1e6)

plot_clustered_barplot(df,
  "scenario",
  "resolution",
  y_label = "Space heating emission",
  y_label_suffix = "MtCO2",
  x_order = sub_scenarios,
  angle_x_label = 90,
  save_path = paste(save_dir, paste0(run, "_tCO2_year_scenario_stack.png"), sep = "/"))

```

### Figures
#### Space heating consumption
```{r}
source("STURM_output/C00_plots.R")

temp <- data %>%
  filter(variable == "heat_kWh") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e9)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Residential space heating consumption in EU\nTWh",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_kWh_countries.png"), sep = "/")
    )

legend <- FALSE
presentation <- TRUE
plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Residential space heating consumption",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    line_types = line_styles_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_kWh_eu.png"), sep = "/"),
    legend = legend,
    y_label_suffix = "TWh",
    presentation = presentation,
    line_order = unname(scenarios))
```

##### Electricity consumption
```{r}
temp <- data %>%
  filter(variable == "heat_kWh") %>%
  filter(resolution %in% c("heat_pump", "electricity")) %>%
  group_by_at(c("region_bld", "year", "scenario")) %>%
  summarize(value = sum(value)) %>%
  ungroup() %>%
  mutate(value = value / 1e9)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Residential space heating electricity consumption in EU\nTWh",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_kWh_electricity_countries.png"), sep = "/"))

legend <- FALSE
presentation <- TRUE
plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Residential space heating electricity consumption in EU\nTWh",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    line_types = line_styles_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_kWh_electricity_eu.png"), sep = "/"),
    y_label_suffix = "TWh",
    legend = legend,
    presentation = presentation,
    line_order = unname(scenarios))
```

##### Standard
```{r}
temp <- data %>%
  filter(variable == "heat_std_kWh") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e9)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Consumtion standard\nTWh",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_std_kWh_countries.png"), sep = "/"))

plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Consumtion standard\nTWh",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    line_types = line_styles_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_std_kWh_eu.png"), sep = "/"),
    y_label_suffix = "TWh")
```

##### Emission
```{r}
source("STURM_output/C00_plots.R")

temp <- data %>%
  filter(variable == "heat_tCO2") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e6)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Residential space heating emission scope 2\nMtCO2",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_tCO2_countries.png"), sep = "/"))

legend <- FALSE
presentation <- TRUE
plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Residential space heating emission scope 2",
    free_y = TRUE,
    line_types = line_styles_scenarios,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_tCO2_eu.png"), sep = "/"),
    legend = legend,
    y_label_suffix = "MtCO2",
    presentation = presentation,
    line_order = unname(scenarios))

```

#### Number of renovations cumulated
```{r}

temp <- data %>%
  filter(variable == "n_renovation") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  group_by(scenario, region_bld) %>%
  arrange(year) %>%
  mutate(value = cumsum(value)) %>%
  ungroup() %>%
  mutate(value = value * 5 / 1e3)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Cumulated number of renovations\nThousand",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_renovation_cumulated_countries.png"), sep = "/"),
    line_order = unname(scenarios))

legend <- FALSE
presentation <- TRUE
plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Cumulated number of renovations\nThousand",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    legend = legend,
    presentation = presentation,
    save_path = paste(save_dir,
      paste0(run, "_renovation_cumulated_eu.png"), sep = "/"),
    line_order = unname(scenarios))
```

#### Number of renovations by income cumulated
```{r}
source("STURM_output/C00_plots.R")

temp <- data %>%
  filter(region_bld == "EU") %>%
  filter(variable == "n_renovation") %>%
  filter(resolution %in% c("q1", "q2", "q3")) %>%
  group_by(scenario, resolution) %>%
  arrange(year) %>%
  mutate(value = cumsum(value)) %>%
  ungroup() %>%
  mutate(value = value * 5 / 1e3) %>%
  select(-c("variable", "region_bld"))


plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "resolution",
    ncol = 3,
    y_label = "Cumulated number of renovations\nThousand",
    free_y = FALSE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_renovation_cumulated_income_eu.png"), sep = "/"))
```

#### Number of renovation
```{r}
temp <- data %>%
  filter(variable == "n_renovation") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e3)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Renovation\nThousands",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_renovation_countries.png"), sep = "/"))

plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Renovation\nThousands",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_renovation_eu.png"), sep = "/"))
```

#### Number of heat-pumps
```{r}
temp <- data %>%
  filter(variable == "stock_building") %>%
  filter(resolution %in% "heat_pump") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e6)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Stock Heat-pumps\nMillion",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_pumps_countries.png"), sep = "/"))

plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Stock Heat-pumps\nMillion",
    free_y = TRUE,
    line_types = line_styles_scenarios,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_heat_pumps_eu.png"), sep = "/"),
    line_order = unname(scenarios))
```


#### Cost of renovation

```{r}
temp <- data %>%
  filter(variable == "cost_renovation_EUR") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e9)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Cost Energy Renovation\nBillion EUR per year",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_cost_renovation_countries.png"), sep = "/"))


legend <- FALSE
presentation <- TRUE
plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Cost Energy Renovation\nBillion EUR per year",
    free_y = TRUE,
    legend = legend,
    presentation = presentation,
    y_label_suffix = "B€/year",
    colors_lines = colors_scenarios,
    line_types = line_styles_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_cost_renovation_eu.png"), sep = "/"),
    line_order = unname(scenarios))
```

#### Cost heating system
```{r}

temp <- data %>%
  filter(variable == "cost_heater_EUR") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e9)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Cost Heating system\nBillion EUR per year",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_cost_heater_countries.png"), sep = "/"))

plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Cost Heating system\nBillion EUR per year",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    line_types = line_styles_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_cost_heater_eu.png"), sep = "/"),
    line_order = unname(scenarios))
```

#### Cost heating 
```{r}
temp <- data %>%
  filter(variable == "cost_heat_EUR") %>%
  filter(resolution %in% "all") %>%
  select(-c("variable", "resolution")) %>%
  mutate(value = value / 1e9)

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Cost Heating\nBillion EUR",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_cost_heat_countries.png"), sep = "/"))

plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Cost Heating\nBillion EURn",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_cost_heat_eu.png"), sep = "/"))

```

### Indicators comparison
#### kWh per square meter
```{r}
var <- "heat_kWh"
ref <- "floor_m2"
path <- "_kwh_m2_countries.png"
y_label <- "Space heating consumption\nkWh per square meter"

temp <- data %>%
  filter(variable %in% c(var, ref)) %>%
  filter(resolution == "all") %>%
  pivot_wider(id_cols = c(region_bld, year, scenario, resolution),
    names_from = variable,
    values_from = value) %>%
  filter(!is.na(.data[[var]])) %>%
  filter(!is.na(.data[[ref]])) %>%
  mutate(value = .data[[var]] / .data[[ref]]) %>%
  select(-c(var, ref, "resolution"))


plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = y_label,
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, path), sep = "/"))

path <- "_kwh_m2_eu.png"
temp <- filter(temp, region_bld == "EU")
plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = y_label,
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, path), sep = "/"))
```

#### kWh per dwelling
```{r}
source("STURM_output/C00_plots.R")

var <- "heat_kWh"
ref <- "stock_building"

temp <- data %>%
  filter(variable %in% c(var, ref)) %>%
  filter(resolution == "all") %>%
  pivot_wider(id_cols = c(region_bld, year, scenario, resolution),
    names_from = variable,
    values_from = value) %>%
  filter(!is.na(.data[[var]])) %>%
  filter(!is.na(.data[[ref]])) %>%
  mutate(value = .data[[var]] / .data[[ref]]) %>%
  select(-c(var, ref, "resolution"))


plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Space heating consumption\nkWh per dwelling",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_kwh_dw_countries.png"), sep = "/"))

path <- "_kwh_dw_eu.png"
temp <- filter(temp, region_bld == "EU")
plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Space heating consumption\nkWh per dwelling",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_kwh_dw_eu.png"), sep = "/"),
    y_label_suffix = "kWh/dw")
```

#### Renovation rate
```{r}
var <- "n_renovation"
ref <- "stock_building"

# filter(temp, region_bld == "EU")

temp <- data %>%
  filter(variable %in% c(var, ref)) %>%
  filter(resolution == "all") %>%
  #filter(region_bld == "EU") %>%
  pivot_wider(id_cols = c(region_bld, year, scenario, resolution),
    names_from = variable,
    values_from = value) %>%
  filter(!is.na(.data[[var]])) %>%
  filter(!is.na(.data[[ref]])) %>%
  mutate(value = .data[[var]] / .data[[ref]]) %>%
  select(-c(var, ref, "resolution"))


plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Renovation rate",
    free_y = FALSE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_renovation_rate_countries.png"), sep = "/"))

presentation <- FALSE
legend <- TRUE
path <- "_renovation_rate_eu.png"
temp <- filter(temp, region_bld == "EU")
plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Renovation rate",
    free_y = FALSE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_renovation_rate_eu.png"), sep = "/"),
    presentation = presentation,
    legend = legend,
    y_label_suffix = "%")
```

#### Energy poverty
```{r}
var <- "energy_poverty_thres"
ref <- "stock_building"
temp <- data %>%
  filter(variable %in% c(var, ref)) %>%
  filter(resolution == "all") %>%
  pivot_wider(id_cols = c(region_bld, year, scenario, resolution),
    names_from = variable,
    values_from = value) %>%
  filter(!is.na(.data[[var]])) %>%
  filter(!is.na(.data[[ref]])) %>%
  mutate(value = .data[[var]] / .data[[ref]]) %>%
  select(-c(var, ref, "resolution")) %>%
  mutate(value = value * 100)


plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "region_bld",
    ncol = 4,
    y_label = "Energy poverty rate (%)",
    free_y = FALSE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_energy_poverty_threshold_countries.png"), sep = "/"),
    y_label_suffix = "%")

legend <- FALSE
presentation <- TRUE
plot_multiple_lines(filter(temp, region_bld == "EU"),
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = NULL,
    ncol = 4,
    y_label = "Energy poverty rate (%)",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_energy_poverty_threshold_eu.png"), sep = "/"),
    y_label_suffix = "%",
    legend = legend,
    presentation = presentation,
    line_types = line_styles_scenarios,
    line_order = unname(scenarios))

```

#### Energy poverty by income class
```{r}
temp <- data %>%
  filter(region_bld == "EU") %>%
  filter(variable == "energy_poverty_thres") %>%
  filter(resolution %in% c("q1", "q2", "q3")) %>%
  mutate(value = value / 1e6) %>%
  select(-c("variable", "region_bld"))

plot_multiple_lines(temp,
    x_column = "year",
    y_column = "value",
    line_column = "scenario",
    group_column = "resolution",
    ncol = 4,
    y_label = "Energy poverty\nMillion",
    free_y = TRUE,
    colors_lines = colors_scenarios,
    save_path = paste(save_dir,
      paste0(run, "_energy_poverty_income.png"), sep = "/"),
    y_label_suffix = "M")

```

### Distributive impact
```{r}
source("STURM_output/C00_plots.R")


years <- c(2030, 2050)
sub_scenarios <- c(
  "Current policies" = "Current policies",
  "Base Mix" = "Base",
  "Enhanced Mix" = "Enhanced",
  # "Enhanced Mix Targetted" = "Targetted",
  "Fossil-Ban Mix" = "Fossil-Ban"
  )

ref <- "Current policies"
rename_income <- c("q1" = "Tertile 1", "q2" = "Tertile 2", "q3" = "Tertile 3")
df <- mutate(data, resolution = ifelse(resolution %in% names(rename_income), rename_income[.data[["resolution"]]], resolution))

budget_share_energy_plots(data, years, sub_scenarios, ref, save_dir, angle_x_label = 20, rename_income = rename_income)

```