---
output: reprex::reprex_document
knit: reprex::reprex_render
---

Notebook to run STURM Ouput.

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(stringr)

print(paste("Working directory is:", getwd()))

# Loding figures setttings and functions
source("STURM_output/C00_plots.R")

dir <- "simulation_2024-06-16_184750"
ref <- "S1"
input_dir <- paste("STURM_output", "figures", dir, sep = "/")
save_dir <- paste(input_dir, "multiple_scenarios", sep = "/")
if (!dir.exists(save_dir)) {
    dir.create(save_dir)
}

file <- paste(input_dir, "results.csv", sep = "/")
data <- read.csv(file,  check.names = FALSE, stringsAsFactors = FALSE, header = TRUE, row.names = NULL)
data <- data[, -1]

emission_saving_counterfactual <- filter(data, scenario_name == ref)$`Emission saving (%)`[1]
energy_saving_counterfactual <- filter(data, scenario_name == ref)$`Consumption saving (%)`[1]
electricity_variation_counterfactual <- filter(data, scenario_name == ref)$`Consumption electricity variation (%)`[1]

data <- data %>%
    mutate(color = "darkgrey") %>%
    mutate(`Emission saving (%)` = ifelse(scenario_name != ref, `Emission saving (%)` + emission_saving_counterfactual, `Emission saving (%)`)) %>%
    mutate(`Consumption saving (%)` = ifelse(scenario_name != ref, `Consumption saving (%)` + energy_saving_counterfactual, `Consumption saving (%)`)) %>%
    mutate(`Consumption electricity variation (%)` = ifelse(scenario_name != ref, `Consumption electricity variation (%)` + electricity_variation_counterfactual, `Consumption electricity variation (%)`)) %>%
    mutate(`Delta total cost (euro/hh/year)` = ifelse(is.na(`Delta total cost (euro/hh/year)`), 0, `Delta total cost (euro/hh/year)`)) %>%
    mutate(`Delta total cost private (euro/hh/year)` = ifelse(is.na(`Delta total cost private (euro/hh/year)`), 0, `Delta total cost private (euro/hh/year)`))


if (FALSE) {
    target_emission_saving <- 0.85
    target_electricity_heating <- 1
    # no social carbon price

    data <- data %>%
        mutate(targets =
        `Emission saving (%)` >= target_emission_saving &
        carbon_tax != "social" &
        `Consumption electricity variation (%)` <= target_electricity_heating) %>%
        mutate(targets = ifelse(targets, "Constraint-Satisfying", "Constraint-Violating")) %>%
        mutate(targets = ifelse(scenario_name == "S1", "No additional policy", targets))
    colors_scenarios <- c("Constraint-Violating" =  "darkgrey", "Constraint-Satisfying" = "darkgreen", "Counterfactual" = "black")

}
min_cost <- min(data$`Delta total cost (euro/hh/year)`, na.rm = TRUE)

data <- data %>%
    mutate(`_success_objective_renovation` = ifelse(is.na(`_success_objective_renovation`), 1, `_success_objective_renovation`)) %>%
    #filter(carbon_tax != "social") %>%
    mutate(groups = "Policy mix") %>%
    mutate(descr = "Policy mix") %>%
    mutate(descr = ifelse(scenario_name == ref, "No additional policy", descr)) %>%
    mutate(descr = ifelse(`Delta total cost (euro/hh/year)` == min_cost, "Cost Minimizing", descr)) %>%
    mutate(groups = ifelse(sub_heat == "carbon" & learning_rate_heat == "", "Heat Pump Maximizing", groups)) %>%
    mutate(groups = ifelse(`_objective_renovation` %in% c("renovation", "deep_renovation"),
        "Renovation Maximizing", groups)) %>%
    mutate(groups = ifelse((groups == "Renovation Maximizing") &
        (sub_heat == "carbon" & learning_rate_heat == ""), "Heat Pump and Renovation Maximizing", groups)) %>%
    mutate(groups = ifelse(scenario_name == ref, "No additional policy", groups)) %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "deep_renovation"
        & `_success_objective_renovation` == 1
        & `_realization_rate_renovation` == 1,
        "All policies", descr))
```

```{r}
data <- data %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "renovation"
        & `_success_objective_renovation` == 0.75
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == FALSE,
        "Renovation", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "renovation"
        & `_success_objective_renovation` == 0.75
        & `_realization_rate_renovation` == 1
        & `_remove_barriers_renovation` == FALSE,
        "Renovation with quality", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "renovation"
        & `_success_objective_renovation` == 0.75
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == TRUE,
        "Renovation without barrier", descr)) %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "renovation"
        & `_success_objective_renovation` == 1
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == FALSE,
        "increased quantity", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "renovation"
        & `_success_objective_renovation` == 1
        & `_realization_rate_renovation` == 1
        & `_remove_barriers_renovation` == FALSE,
        "increased quantity with quality", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "renovation"
        & `_success_objective_renovation` == 1
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == TRUE,
        "increased quantity without barrier", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "deep_renovation"
        & `_success_objective_renovation` == 0.75
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == FALSE,
        "improved depth", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "deep_renovation"
        & `_success_objective_renovation` == 0.75
        & `_realization_rate_renovation` == 1
        & `_remove_barriers_renovation` == FALSE,
        "improved depth with quality", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon" & learning_rate_heat == "" & carbon_tax == "EUETS"
        & `_objective_renovation` == "deep_renovation"
        & `_success_objective_renovation` == 0.75
        & `_realization_rate_renovation` == 1
        & `_remove_barriers_renovation` == TRUE,
        "improved depth without barrier", descr))  %>%
    mutate(descr = ifelse(sub_heat == "carbon"
        & learning_rate_heat == ""
        & carbon_tax == ""
        & `_objective_renovation` == ""
        & `_realization_rate_renovation` == 1
        & `_remove_barriers_renovation` == FALSE, "Heat pumps max with quality", descr)) %>%
    mutate(descr = ifelse(sub_heat == "carbon"
        & learning_rate_heat == ""
        & carbon_tax == ""
        & `_objective_renovation` == ""
        & `_realization_rate_renovation` == 1
        & `_remove_barriers_renovation` == TRUE, "Heat pumps max without barrier", descr))


data <- data %>%
    mutate(groups = ifelse(groups == "Heat Pump and Renovation Maximizing", "Heat Pump Maximizing", groups)) %>%
    mutate(groups = ifelse(groups == "Renovation Maximizing", "Policy mix", groups)) %>%
    mutate(descr = ifelse(scenario_name == ref, "No additional policy", descr)) %>%
    mutate(descr = ifelse(sub_heat == "carbon"
        & learning_rate_heat == ""
        & carbon_tax == ""
        & `_objective_renovation` == ""
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == FALSE, "Heat pumps max", descr)) %>%
    mutate(descr = ifelse(sub_heat == ""
        & learning_rate_heat == ""
        & carbon_tax == ""
        & `_objective_renovation` == ""
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == FALSE, "Heat pumps only learning", descr)) %>%
    mutate(descr = ifelse(sub_heat == "half_carbon"
        & learning_rate_heat == ""
        & carbon_tax == ""
        & `_objective_renovation` == ""
        & `_realization_rate_renovation` == 0.75
        & `_remove_barriers_renovation` == FALSE, "Heat pumps medium", descr))



# is.na(`_success_objective_renovation`) & `_realization_rate_renovation` == 1 & 
    #"Heat Pump Maximizing policy mix", groups)) %>%
colors_scenarios <- c(
    "No additional policy" = "black",
    "Policy mix" = "darkgrey",
    "Heat Pump Maximizing" = "darkgreen",
    "Renovation Maximizing" = "darkblue",
    "Heat Pump and Renovation Maximizing" = "darkred"
    )

scenarios_shape <- c(
    "No additional policy" = 8,
    "Policy mix" = 16,
    "Heat Pump Maximizing" = 17,
    "Renovation Maximizing" = 18,
    "Heat Pump and Renovation Maximizing" = 15
)

```



##### Histogram - Distribution of key outcomes across scenarios
```{r}
source("STURM_output/C00_plots.R")

column <- "Consumption saving (%)"
save_path <- paste(save_dir, "Consumption_saving.png", sep = "/")
plot_histogram(data, column, save_path)

column <- "Emission saving (%)"
save_path <- paste(save_dir, "Emission_saving.png", sep = "/")
plot_histogram(data, column, save_path)

column <- "Consumption electricity variation (%)"
save_path <- paste(save_dir, "Electricity_variation.png", sep = "/")
plot_histogram(data, column, save_path)

column <- "Delta total cost private (euro/hh/year)"
save_path <- paste(save_dir, "Delta_total_cost_private_euro_hh_year.png", sep = "/")
plot_histogram(data, column, save_path)


# TODO: histogram cost-efficient strategies
```
#------------------------------------------------------------------------------
##### Sobol - Identification of key policies
```{r}
# Sobol analysis
source("STURM_output/C00_plots.R")

rename_policies <- c("carbon_tax" = "Carbon tax",
    "sub_heat" = "Heat pump subsidies",
    "learning_rate_heat" = "Heat pump learning-by-doing",
    #"_remove_barriers_heater" = "Market-failures heating system",
    "_objective_renovation" = "Energy renovation",
    "_realization_rate_renovation" = "Renovation realization rate",
    "_remove_barriers_renovation" = "Market-failures energy renovation"
    )
list_policies <- c("carbon_tax",
    "_objective_renovation",
    "sub_heat", "learning_rate_heat", "_realization_rate_renovation",
    "_remove_barriers_renovation"#, "_remove_barriers_heater"
    )

list_features <- list_policies
df <- data %>%
    filter(`_success_objective_renovation`== 1) %>%
    filter(scenario_name != ref) %>%
    # Replace NaN or empty value by "no" for all 
    mutate(across(all_of(list_policies), ~ifelse(is.na(.x) | .x == "", "no", .x))) %>%
    mutate(`_remove_barriers_renovation` = ifelse(`_remove_barriers_renovation`, "yes", "no"))
    


y <- "Emission (MtCO2)"
save_path <- paste(save_dir, "sobol_analysis_emission.png", sep = "/")
sobol_figures(df, list_policies, y, rename_policies, save_path)

y <- "Space heating consumption (TWh)"
save_path <- paste(save_dir, "sobol_analysis_energy.png", sep = "/")
sobol_figures(df, list_policies, y, rename_policies, save_path)

y <- "Delta total cost private (euro/hh/year)"
save_path <- paste(save_dir, "sobol_analysis_cost.png", sep = "/")
sobol_figures(df, list_policies, y, rename_policies, save_path)

```



#------------------------------------------------------------------------------
##### Scatter plot - Relationship between two key outcomes
```{r}
source("STURM_output/C00_plots.R")
x_column <- "Delta total cost (euro/hh/year)"
y_column <- "Emission saving (%)"
#color_column <- "descr"
color_column <- "groups"
shape_column <- "groups"

save_path <- paste(save_dir, "tradeoff_cost_emission.png", sep = "/")

temp <- data %>%
    mutate(`Emission saving (%)` = 100 * `Emission saving (%)`)

scatter_plots(temp,
            x_column,
            y_column,
            color_column,
            colors_scenarios = colors_scenarios,
            size_column = NULL,
            shape_column = shape_column,
            scenarios_shape = scenarios_shape,
            hline = 95,
            save_path = save_path,
            x_label_suffix = "€",
            y_label_suffix = "%",
            legend_suffix = "",
            y_label = "Emission saving (%)",
            x_label = "Social cost-benefits (€/hh/year)",
            legend = TRUE,
            presentation = FALSE)

```


```{r}
x_column <- "Delta total cost private (euro/hh/year)"
y_column <- "Emission saving (%)"

save_path <- paste(save_dir, "tradeoff_cost_private_emission.png", sep = "/")

temp <- data %>%
    mutate(`Emission saving (%)` = 100 * `Emission saving (%)`)

source("STURM_output/C00_plots.R")
scatter_plots(temp,
            x_column,
            y_column,
            color_column,
            colors_scenarios = colors_scenarios,
            size_column = NULL,
            shape_column = shape_column,
            scenarios_shape = scenarios_shape,
            save_path = save_path,
            hline = 95,
            x_label_suffix = "",
            y_label_suffix = "%",
            legend_suffix = "",
            y_label = "Emission saving (%)",
            x_label = "Private cost-benefits (€/hh/year)",
            legend = TRUE,
            presentation = FALSE)
```

```{r}
x_column <- "Consumption electricity variation (%)"
y_column <- "Emission saving (%)"

save_path <- paste(save_dir, "tradeoff_electricity_emission.png", sep = "/")

temp <- data %>%
    mutate(`Emission saving (%)` = 100 * `Emission saving (%)`) %>%
    mutate(`Consumption electricity variation (%)` = 100 * `Consumption electricity variation (%)`)

scatter_plots(temp,
            x_column,
            y_column,
            color_column,
            hline = 95,
            colors_scenarios = colors_scenarios,
            size_column = NULL,
            shape_column = shape_column,
            scenarios_shape = scenarios_shape,
            save_path = save_path,
            x_label_suffix = "%",
            y_label_suffix = "%",
            legend_suffix = "",
            y_label = "Emission saving (%)",
            x_label = "Electricitity use variation (%)",
            legend = TRUE,
            presentation = FALSE)
```


```{r}
x_column <- "Consumption saving (%)"
y_column <- "Emission saving (%)"

save_path <- paste(save_dir, "tradeoff_consumption_emission.png", sep = "/")

temp <- data %>%
    mutate(`Consumption saving (%)` = 100 * `Consumption saving (%)`) %>%
    mutate(`Emission saving (%)` = 100 * `Emission saving (%)`)

scatter_plots(temp,
            x_column,
            y_column,
            color_column,
            hline = 95,
            colors_scenarios = colors_scenarios,
            size_column = NULL,
            shape_column = shape_column,
            scenarios_shape = scenarios_shape,
            save_path = save_path,
            x_label_suffix = "%",
            y_label_suffix = "%",
            legend_suffix = "",
            y_label = "Emission saving (%)",
            x_label = "Consumption saving (%)",
            legend = TRUE,
            presentation = FALSE)

```




```{r}
# Scenario to assess
scenarios_heat_pumps <- c("No additional policy", "Heat pumps only learning", "Heat pumps medium", "Heat pumps max")
scenarios_heat_pumps_names <- data %>%
    filter(descr %in% scenarios_heat_pumps) %>%
    select(scenario_name, descr)
scenarios_heat_pumps_names <- setNames(scenarios_heat_pumps_names$descr, scenarios_heat_pumps_names$scenario_name)

scenarios_renovation <- c(
    "Heat pumps max", "Renovation", "increased quantity", "improved depth",
    "Heat pumps max with quality", "Renovation with quality", "increased quantity with quality", "improved depth with quality",
    "Heat pumps max without barrier", "Renovation without barrier", "increased quantity without barrier", "improved depth without barrier"
    )

scenario_renovation_names <- data %>%
    filter(descr %in% scenarios_renovation) %>%
    select(scenario_name, descr)
scenario_renovation_names <- setNames(scenario_renovation_names$descr, scenario_renovation_names$scenario_name)

```

#------------------------------------------------------------------------------
#------------------------------------------------------------------------------
#### Analysis by countries

```{r}
file <- "STURM_data/input_csv/input_resid/decision/cost_factor_countries_EU.csv"
cost_factor <- read.csv(file,  check.names = FALSE, stringsAsFactors = FALSE, header = TRUE, row.names = NULL) %>%
    mutate(region_bld = rename_countries[region_bld]) %>%
    rename(name = region_bld, cost_factor = value)


file <- "2024-06-16_184750_2050_summary_countries.csv"
file <- paste(input_dir, file, sep = "/")
data_eu <- read.csv(file,  check.names = FALSE, stringsAsFactors = FALSE, header = TRUE, row.names = NULL) %>%
    mutate(name = `Member states`) %>%
    # Normalize the cost factor
    left_join(cost_factor) %>%
    mutate(cost_factor = ifelse(is.na(cost_factor), 1, cost_factor)) %>%
    mutate(
        `Cost renovation (Billion EUR)` = `Cost renovation (Billion EUR)` / cost_factor,
        `Cost heater (Billion EUR)` = `Cost heater (Billion EUR)` / cost_factor,
        `Total cost (Billion EUR)` = `Total cost (Billion EUR)` / cost_factor,
        `Government expenditures (Billion EUR)` = `Government expenditures (Billion EUR)` / cost_factor
        ) %>%
    # Add per capita values
    mutate(
        `Space heating consumption (MWh/capita)` = `Space heating consumption (TWh)` / `Population (Million)`,
        `Space heating consumption electricity (MWh/capita)` = `Space heating consumption electricity (TWh)` / `Population (Million)`,
        `Emission (tCO2/capita)` = `Emission (MtCO2)` / `Population (Million)`,
        `Cost renovation (EUR/capita)` = `Cost renovation (Billion EUR)` / `Population (Million)`,
        `Cost heater (EUR/capita)` = `Cost heater (Billion EUR)` / `Population (Million)`,
        `Government expenditures (Billion EUR)` = `Government expenditures (Billion EUR)` / `Population (Million)`,
    ) %>%
    mutate(name = ifelse(name == "Czech Republic", "Czechia", name))

data_eu <- data_eu %>%
    mutate(scenario_name = ifelse(scenario_name %in% names(scenarios_heat_pumps_names), scenarios_heat_pumps_names[scenario_name], scenario_name)) %>%
    mutate(scenario_name = ifelse(scenario_name %in% names(scenario_renovation_names), scenario_renovation_names[scenario_name], scenario_name))


file <- "results_countries.csv"
file <- paste(input_dir, file, sep = "/")
result_eu <- read.csv(file,  check.names = FALSE, stringsAsFactors = FALSE, header = TRUE, row.names = NULL) %>%
    rename(name = `Member states`) %>%
    mutate(name = ifelse(name == "Czech Republic", "Czechia", name))
```

#-----------------------------------------------------------------------------------------
#### Maps

## Heat pumps scenarios
```{r}
source("STURM_output/C00_plots.R")

df <- data_eu %>%
    select(c("scenario_name", "Share fossil-fuels (Percent)", "name")) %>%
    rename(value = `Share fossil-fuels (Percent)`) %>%
    mutate(value = ifelse(is.na(value), 0, value)) %>%
    #rename(name = `Member states`) %>%
    filter(scenario_name %in% c("Initial", "No additional policy"))

min <- min(df$value, na.rm = TRUE)
limits <- c(-0.5, 0)
save_path <- paste(save_dir, "maps_fossil_countries.png", sep = "/")

plot_map(df,
        limits = NULL,
        threshold_colormap = NULL,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        ncol = 4,
        key = "name")
```

```{r}
source("STURM_output/C00_plots.R")

temp <- data_eu %>%
    select(c("scenario_name", "name", "Emission saving (%)")) %>%
    rename(value = `Emission saving (%)`) %>%
    filter(scenario_name %in% scenarios_heat_pumps)

temp$scenario_name <- factor(temp$scenario_name, levels = scenarios_heat_pumps)

min <- min(temp$value, na.rm = TRUE)
limits <- c(min, 1)
save_path <- paste(save_dir, "maps_emission_countries_heatpump.png", sep = "/")

plot_map(temp,
        limits,
        threshold_colormap = 0.95,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        ncol = 4,
        key = "name")
```

#-----------------------------------------------------------------------------------------
# Renovation

# 1. Cost-benefits analysis
```{r}
source("STURM_output/C00_plots.R")
var <- "Delta total cost (euro/hh/year)"
df <- result_eu %>%
    select(c("scenario_name", "name", "variable", "value")) %>%
    filter(variable == var) %>%
    filter(scenario_name %in% names(scenario_renovation_names)) %>%
    mutate(scenario_name = scenario_renovation_names[scenario_name])

ref_heat_pump <- df %>%
    filter(variable == var) %>%
    filter(scenario_name %in% c("Heat pumps max", "Heat pumps max with quality")) %>%
    pivot_wider(names_from = "scenario_name", values_from = "value")
    
df <- df %>%
    filter(!scenario_name %in% c("Heat pumps max", "Heat pumps max with quality")) %>%
    left_join(ref_heat_pump) %>%
    mutate(value = ifelse(grepl("quality", scenario_name), value - `Heat pumps max with quality`, value - `Heat pumps max`))

df$scenario_name <- factor(df$scenario_name, levels = scenario_renovation_names)

save_path <- paste(save_dir, "maps_cba_countries_renovation.png", sep = "/")

plot_map(df,
        limits = NULL,
        threshold_colormap = 0,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        reverse_colormap = TRUE,
        ncol = 3,
        key = "name")
```

# 2. Electricity consumption



```{r}
source("STURM_output/C00_plots.R")


scenarios_poverty <- c("Initial", "No additional policy", "Heat pumps max", "improved depth with quality")
temp <- data_eu %>%
    select(c("scenario_name", "name", "Space heating consumption electricity (MWh/capita)")) %>%
    rename(value = `Space heating consumption electricity (MWh/capita)`) %>%
    filter(scenario_name %in% scenarios_poverty)

temp$scenario_name <- factor(temp$scenario_name, levels = scenarios_poverty)

#min <- min(temp$value, na.rm = TRUE)
#
save_path <- paste(save_dir, "maps_electricity_countries_electricity.png", sep = "/")

limits <- c(0, 1)

plot_map(temp,
        limits = NULL,
        threshold_colormap = NULL,
        figure_title = "",
        save_path = save_path,
        legend_title = "MWh/capita",
        subplot_column = "scenario_name",
        ncol = 4,
        key = "name")
```

# 3. Energy poverty

```{r}
source("STURM_output/C00_plots.R")


scenarios_poverty <- c("Initial", "No additional policy", "Heat pumps max", "improved depth with quality")
temp <- data_eu %>%
    select(c("scenario_name", "name", "Energy poverty (Percent)")) %>%
    rename(value = `Energy poverty (Percent)`) %>%
    filter(scenario_name %in% scenarios_poverty)

temp$scenario_name <- factor(temp$scenario_name, levels = scenarios_poverty)

#min <- min(temp$value, na.rm = TRUE)
#
save_path <- paste(save_dir, "maps_electricity_countries_poverty.png", sep = "/")

limits <- c(0, 0.2)

plot_map(temp,
        limits = limits,
        threshold_colormap = NULL,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        ncol = 4,
        key = "name")
```

#----------------------------------
# Maximum scenario by EU member states

```{r}
var <- "Delta total cost (euro/hh/year)"

temp <- setNames(names(rename_countries), rename_countries)

df <- result_eu %>%
    select(c("scenario_name", "name", "variable", "value")) %>%
    filter(variable == var) %>%
    group_by(name) %>%
    summarize(scenario_name = scenario_name[which.min(value)]) %>%
    ungroup() %>%
    mutate(name = ifelse(name == "Czechia", "Czech Republic", name)) %>%
    mutate(name = temp[name]) %>%
    rename(region_bld = name) %>%
    filter(region_bld != "EU")

write.csv(df, paste(save_dir, "first_best_scenario.csv", sep = "/"), row.names = FALSE)

df <- result_eu %>%
    filter(carbon_tax != "social") %>%
    filter(`_remove_barriers_renovation` == FALSE) %>%
    filter() %>%
    select(c("scenario_name", "name", "variable", "value")) %>%
    filter(variable == var) %>%
    group_by(name) %>%
    summarize(scenario_name = scenario_name[which.min(value)]) %>%
    ungroup() %>%
    mutate(name = ifelse(name == "Czechia", "Czech Republic", name)) %>%
    mutate(name = temp[name]) %>%
    rename(region_bld = name) %>%
    filter(region_bld != "EU")

write.csv(df, paste(save_dir, "second_best_scenario.csv", sep = "/"), row.names = FALSE)


df <- result_eu %>%
    filter(carbon_tax != "social") %>%
    filter(`_remove_barriers_renovation` == FALSE) %>%
    filter(learning_rate_heat == "constant") %>%
    filter(`_realization_rate_renovation` == 1) %>%
    filter() %>%
    select(c("scenario_name", "name", "variable", "value")) %>%
    filter(variable == var) %>%
    group_by(name) %>%
    summarize(scenario_name = scenario_name[which.min(value)]) %>%
    ungroup() %>%
    mutate(name = ifelse(name == "Czechia", "Czech Republic", name)) %>%
    mutate(name = temp[name]) %>%
    rename(region_bld = name) %>%
    filter(region_bld != "EU")

write.csv(df, paste(save_dir, "constraint_scenario.csv", sep = "/"), row.names = FALSE)

```


```{r}
source("STURM_output/C00_plots.R")

temp <- data_eu %>%
    select(c("scenario_name", "name", "Consumption electricity variation (%)")) %>%
    rename(value = `Consumption electricity variation (%)`) %>%
    filter(scenario_name %in% scenario_renovation_names)

temp$scenario_name <- factor(temp$scenario_name, levels = scenario_renovation_names)

min <- min(temp$value, na.rm = TRUE)
#limits <- c(min, 1)
save_path <- paste(save_dir, "maps_electricity_countries_renovation.png", sep = "/")

plot_map(temp,
        limits = NULL,
        threshold_colormap = NULL,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        ncol = 3,
        key = "name")
```


```{r}
source("STURM_output/C00_plots.R")

cost_heat_pump_max <- data_eu %>%
    filter(scenario_name == "Heat pumps max") %>%


temp <- data_eu %>%
    select(c("scenario_name", "name", "Consumption electricity variation (%)")) %>%
    rename(value = `Consumption electricity variation (%)`) %>%
    filter(scenario_name %in% scenario_renovation_names)

temp$scenario_name <- factor(temp$scenario_name, levels = scenario_renovation_names)

min <- min(temp$value, na.rm = TRUE)
#limits <- c(min, 1)
save_path <- paste(save_dir, "maps_electricity_countries_renovation.png", sep = "/")

plot_map(temp,
        limits = NULL,
        threshold_colormap = NULL,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        ncol = 3,
        key = "name")
```



```{r}
source("STURM_output/C00_plots.R")

temp <- df %>%
    select(c("scenario_name", "name", "Space heating consumption (MWh/capita)")) %>%
    rename(value = `Space heating consumption (MWh/capita)`) %>%
    filter(scenario_name %in% scenarios)

temp$scenario_name <- factor(temp$scenario_name, levels = scenarios)

limits <- c(0, 7)
save_path <- paste(save_dir, "space_heating_consumption_countries.png", sep = "/")

plot_map(temp,
        limits,
        figure_title = "",
        save_path = save_path,
        legend_title = "MWh/capita",
        subplot_column = "scenario_name",
        ncol = 3,
        key = "name")
```

```{r}
source("STURM_output/C00_plots.R")

temp <- df %>%
    select(c("scenario_name", "name", "Share fossil-fuels (Percent)")) %>%
    rename(value = `Share fossil-fuels (Percent)`) %>%
    mutate(value = ifelse(is.na(value), 0, value)) %>%
    filter(scenario_name %in% scenarios)

temp$scenario_name <- factor(temp$scenario_name, levels = scenarios)

limits <- c(0, 0.8)
save_path <- paste(save_dir, "share_fossil_fuels_countries.png", sep = "/")

plot_map(temp,
        limits,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "scenario_name",
        ncol = 3,
        key = "name")
```

### Calculate difference compared to the S1 the counterfactual
```{r}

rename_variable <- c("Space heating consumption (TWh)" = "Energy consumption",
    "Emission (MtCO2)" = "Emission",
    "Cost renovation (Billion EUR)" = "Renovation investment",
    "Cost heater (Billion EUR)" = "Heating system investment")

variables <- c("Space heating consumption (TWh)", "Emission (MtCO2)")#, "Cost renovation (Billion EUR)", "Cost heater (Billion EUR)")
diff_counterfactual_eu <- data_eu %>%
    filter(scenario_name %in% c("S1", best_scenario)) %>%
    select(all_of(c("scenario_name", "name", variables))) %>%
    pivot_longer(cols = all_of(variables),
                names_to = "variable",
                values_to = "value") %>%
    pivot_wider(names_from = "scenario_name", values_from = "value") %>%
    mutate(value = (.data[[best_scenario]] - .data[["S1"]]) / .data[["S1"]]) %>%
    mutate(variable = rename_variable[variable])
```

```{r}
limits <- c(-1, 0)
save_path <- paste(save_dir, "effort_countries.png", sep = "/")

plot_map(diff_counterfactual_eu,
        limits,
        figure_title = "",
        save_path = save_path,
        legend_title = "%",
        subplot_column = "variable",
        ncol = 4,
        key = "name")
```



```{r}
rename_variable <- c("Emission saving (%)" = "Emission saving",
    "Consumption saving (%)" = "Emission",
    "Cost renovation (Billion EUR)" = "Renovation investment",
    "Cost heater (Billion EUR)" = "Heating system investment")

variables <- c("Emission saving (%)", "Consumption saving (%)", "Consumption electricity variation (%)")
diff_avg_eu <- data_eu %>%
    filter(scenario_name == best_scenario) %>%
    select(all_of(c("name", variables))) %>%
    pivot_longer(cols = all_of(variables),
                names_to = "variable",
                values_to = "value") %>%
    group_by(variable) %>%
    mutate(average = mean(value)) %>%
    ungroup() %>%
    # Compare to average value accross countries
    mutate(value = (.data[[best_scenario]] - .data[[best_scenario]]) / .data[[best_scenario]]) %>%
    mutate(value = (.data[[best_scenario]] - .data[["S1"]]) / .data[["S1"]]) %>%
    mutate(variable = rename_variable[variable])


```


### Calculate difference compared to the S1 the counterfactual
```{r}

rename_variable <- c("Space heating consumption (MWh/capita)" = "Energy reduction effort",
    "Emission (tCO2/capita)" = "Emission reduction effort",
    "Cost renovation (EUR/capita)" = "Cost renovation effort",
    "Cost heater (EUR/capita)" = "Cost heater effort")

variables <- c("Space heating consumption (MWh/capita)", "Emission (tCO2/capita)",
    "Cost renovation (EUR/capita)", "Cost heater (EUR/capita)")#, "Cost renovation (Billion EUR)", "Cost heater (Billion EUR)")
diff_counterfactual_eu <- data_eu %>%
    filter(scenario_name %in% c("S1", best_scenario)) %>%
    select(all_of(c("scenario_name", "name", variables))) %>%
    pivot_longer(cols = all_of(variables),
                names_to = "variable",
                values_to = "value") %>%
    pivot_wider(names_from = "scenario_name", values_from = "value") %>%
    mutate(effort = (.data[[best_scenario]] - .data[["S1"]])) %>%
    group_by(variable) %>%
    mutate(avg_effort = mean(effort)) %>%
    ungroup() %>%
    mutate(value = effort / avg_effort) %>%
    mutate(variable = ifelse(variable %in% names(rename_variable), rename_variable[variable], variable))
```

```{r}
limits <- c(-2, 2)
save_path <- paste(save_dir, "effort_countries.png", sep = "/")

plot_map(diff_counterfactual_eu,
        limits,
        figure_title = "",
        save_path = save_path,
        legend_title = "Effort compared to average",
        subplot_column = "variable",
        ncol = 2,
        key = "name")

```

#------------------------------------------------------------------------------
#### Old: Identification of policies that are in the target
```{r}
# Identify the policies that are in the target


rename_policies <- c("carbon_tax" = "Carbon tax",
    "sub_heat" = "Heat pump subsidies",
    "learning_rate_heat" = "Heat pump learning-by-doing",
    "_remove_barriers_heater" = "Policies tackling market-failures heating system",
    "_objective_renovation" = "Energy renovation subsidies",
    "_realization_rate_renovation" = "Renovation realization rate",
    "_remove_barriers_renovation" = "Market-failures energy renovation")

list_policies <- c("carbon_tax", "_objective_renovation",
    "sub_heat", "learning_rate_heat", "_realization_rate_renovation",
    "_remove_barriers_renovation", "_remove_barriers_heater")
list_policies <- intersect(list_policies, colnames(data))

temp <- data %>%
    filter(`Emission saving (%)` > 0.95) %>%
    # Select only the policies that are in data colnames
    select(all_of(list_policies)) %>%
    mutate(across(all_of(list_policies), as.character)) %>%
    pivot_longer(cols = all_of(list_policies),
                names_to = "policy", 
                values_to = "value") %>%
    # replace "" by "No"
    mutate(value = ifelse(value == "", "No", value))

# Add a count column for position adjustment
n_scenario <- nrow(temp)
temp <- temp %>%
  group_by(policy, value) %>%
  summarise(count = n()) #/ n_scenario)


# Make stacked bar plot of the policies in the target scenarios
p <- temp %>%
    mutate(policy = rename_policies[policy]) %>%
    ggplot(aes(y = policy, fill = value)) +
    geom_bar(position = "fill") +
    geom_text(aes(label = value, x = 1), 
            position = position_fill(vjust = 0.5), 
            size = 6, 
            color = "white") +
    message_building_theme +
    # No legend
    theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

save_path <- paste(save_dir, "policies_condition.png", sep = "/")
ggsave(save_path, plot = p, width = plot_settings[["width"]],
        height = plot_settings[["height"]],
        dpi = plot_settings[["dpi"]])

``` 
```{r}
# Calculate the average cost accoss scenarios

# temp <- data_eu %>%
#     filter(scenario_name %in% scenarios_target) %>%
#     group_by_at("Member states") %>%
#     summarize(`Emission saving (%)` = mean(`Emission saving (%)`),
#         `Consumption saving (%)` = mean(`Consumption saving (%)`),
#         `Consumption electricity variation (%)` = mean(`Consumption electricity variation (%)`),
#         `Renovated buildings (#/capita)` = mean(`Renovated buildings (Million)` / `Population (Million)`),
#         `Heat-pumps (#/capita)` = mean(`Heat-pumps (Million)` / `Population (Million)`),
#         `Space heating consumption (MWh/capita)` = mean(`Space heating consumption (TWh)` / `Population (Million)`),
#         `Emission (tCO2/capita)` = mean(`Emission (MtCO2)` / `Population (Million)`),
#         `Government expenditures (EUR/capita)`= mean(`Government expenditures (Billion EUR)` / `Population (Million)`),
#         `Cost renovation (EUR/capita)` = mean(`Cost renovation (Billion EUR)` / `Population (Million)`),
#         `Cost heater (EUR/capita)` = mean(`Cost heater (Billion EUR)` / `Population (Million)`),
#         `Total cost (EUR/capita)`= mean(`Total cost (Billion EUR)` / `Population (Million)`))


# write.csv(temp, paste(save_dir, "scenario_target_countries.csv", sep = "/"), row.names = FALSE)

```

```{r}
source("STURM_output/C00_plots.R")
var <- "Total cost"
ref_maps <- "Heat pumps max"
cost_ref <- data_cba_eu %>%
    filter(variable == var) %>%
    filter(scenario_name == ref_maps)
cost_ref <- setNames(cost_ref$value, cost_ref$name)

ref_quality_maps <- "Heat pumps max with quality"
cost_ref_quality <- data_cba_eu %>%
    filter(variable == var) %>%
    filter(scenario_name == ref_quality_maps)
cost_ref_quality <- setNames(cost_ref_quality$value, cost_ref_quality$name)

ref_barrier_maps <- "Heat pumps max without barrier"
cost_ref_barrier <- data_cba_eu %>%
    filter(variable == var) %>%
    filter(scenario_name == ref_barrier_maps)
cost_ref_barrier <- setNames(cost_ref_barrier$value, cost_ref_barrier$name)


temp <- data_cba_eu %>%
  filter(variable == var) %>%
  filter(scenario_name %in% scenario_renovation_names) %>%
  filter(!grepl("barrier", scenario_name)) %>%
  filter(scenario_name != ref_maps) %>%
  filter(scenario_name != ref_quality_maps) %>%
  filter(scenario_name != ref_barrier_maps) %>%
  mutate(value = case_when(
    grepl("quality", scenario_name) ~ value - cost_ref_quality[name],
    grepl("barrier", scenario_name) ~ value - cost_ref_barrier[name],
    TRUE ~ value - cost_ref[name]
  ))

temp$scenario_name <- factor(temp$scenario_name, levels = scenario_renovation_names)

min_maps <- min(filter(temp, variable == var)$value, na.rm = TRUE)
max_maps <- max(filter(temp, variable == var)$value, na.rm = TRUE)
limits <- c(min_maps, max_maps)
figure_title <- "Cost"
legend_title <- "€/hh.year"
title <- "cost"
save_path <- paste(save_dir, "maps_cba_countries_renovation.png", sep = "/")


plot_map(temp,
  limits,
  threshold_colormap = 0,
  figure_title = figure_title,
  legend_title = legend_title,
  reverse_colormap = TRUE,
  subplot_column = "scenario_name",
  ncol = 3,
  save_path = save_path,
  key = "name")

```


```{r}
source("STURM_output/C00_plots.R")
file <- "data_cba_country.csv"
file <- paste(input_dir, file, sep = "/")
data_cba_eu <- read.csv(file,  check.names = FALSE, stringsAsFactors = FALSE, header = TRUE, row.names = NULL)  %>%
    rename(scenario_name = scenario) %>%
    rename(name = region_bld) %>%
    mutate(name = ifelse(name %in% names(rename_countries), rename_countries[name], name)) %>%
    mutate(scenario_name = ifelse(scenario_name %in% names(scenarios_heat_pumps_names), scenarios_heat_pumps_names[scenario_name], scenario_name)) %>%
    mutate(scenario_name = ifelse(scenario_name %in% names(scenario_renovation_names), scenario_renovation_names[scenario_name], scenario_name))
```

